Document knowledge base linking for information retrieval

### 2016-05-07 paper.tex
squeezed onto 4 pages

We obtain a list of candidate entities by running $Q_D$ over an index of our knowledge base, $C_E$, where each entry in this index is the text of an entity $E$'s knowledge base node. More formally, we rank the entities in our knowledge base against $D$ using Eq. \ref{equation.ql}, substituting $Q_D$ for the query and $E_i$---the text of the $i^{th}$ entity---for the document. Let $\pi_i$ be the log-probability for entity $E_i$ with respect to $D$ given by Eq. \ref{equation.ql}.

@@

To perform knowledge base linking, we make use of the September 1, 2015 dump of English Wikipedia. We build an Indri\footnote{http://www.lemurproject.org/indri/} index over the Wikipedia page text. The text of each Wikipedia page also serves as the ``description text'' used in Eq. \ref{eq.entity-sum}.

We test our approach using the TREC 2004 robust topics. These 250 topics are used with data from TREC disks 4 and 5. In addition, we use the AP newswire collection from TREC disks 1 and 2 with topics 101-200. Using slightly older test collections helps to ensure that the knowledge base's coverage includes information about the topics; as noted in \cite{Frank2013}, updates to knowledge bases may lag considerably behind the occurrence of events.

For comparison, we also report the results of our model using entity links produced by Apache Stanbol\footnote{http://stanbol.apache.org/}. We process the test collections with Stanbol's default ``enhancer,'' which supplies entity links and corresponding confidence scores. Though Stanbol links to DBpedia\footnote{http://dbpedia.org} resources, these generally correspond to Wikipedia pages and may be converted easily. We select the link with the highest confidence for each mention in a given document and limit the set of links to $n$, the number of entities used in our bag-of-links approach. These links form the set of document links, and their confidence scores may be normalized to provide an estimate of $P(E|D)$.

@@

We remove stop words in documents and entity descriptions for all runs. For the \textit{kb} and \textit{stanbol} runs, we retrieve the top 1000 documents per query based on the default Indri query likelihood implementation. We then re-rank these documents by incorporating their knowledge base links as described in Section \ref{section.model}.

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|c|p{0.29\textwidth}|c|} \hline
{\bf Param} & {\bf Meaning} & {\bf Value} \\ \hline
$k$ & The maximum number of document terms to use in constructing $Q_D$. & 20 \\ \hline
$n$ & The maximum number of knowledge base entries in $\mathcal{E}_D$. & 10-100 \\ \hline
$\lambda$ & Mixing parameter controlling the weights of $P(q|D)$ and $P(q|E)$ & 0.0-1.0 \\ \hline
$\mu$ & Used for Dirichlet smoothing of both $P(q|D)$ and $P(q|E)$. & 2500 \\ \hline
%$fbDocs$ & The number of feedback documents to use for RM3 runs. & 20 \\ \hline
%$fbTerms$ & The number of terms per document to use for RM3 runs. & 20 \\ \hline
%$\alpha$ & Mixing parameter controlling the weights of the original query and relevance model for RM3 runs. & 0.5 \\ \hline
\end{tabular}
\caption{Parameter settings for the entity linking procedure and retrieval model}
\label{table.parameters}
\end{table}

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|c|l|c|c|c|} \hline
& {\bf Run} & {\bf $\lambda$} & {\bf $n$} & {\bf MAP} \\ \hline
\rule{0pt}{2.5ex} \multirow{3}{*}{Robust} & {\it baseline-ql} & -- & -- & 0.2183 \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it kb-ql} & 0.2 & 10 & 0.2354$^{\uparrow}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it stanbol-ql} & 0.1 & -- & 0.2194 \\ \hline
\rule{0pt}{2.5ex} \multirow{3}{*}{AP} & {\it baseline-ql} & -- & -- & 0.2346 \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it kb-ql} & 0.2 & 20 & 0.2680$^{\uparrow}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it stanbol-ql} & 0.1 & -- & 0.2355 \\ \hline
\end{tabular}
\caption{The top-scoring runs and baselines by MAP. Values marked with $\uparrow$ are statistically significant improvements over baselines.}
\label{table.performance}
\end{table}

\begin{figure*}
\centering
\begin{subfigure}{\columnwidth}
\centering
\includegraphics[width=\columnwidth]{figures/sweep-entities-AP.pdf}
\end{subfigure}%
\begin{subfigure}{\columnwidth}
\centering
\includegraphics[width=\columnwidth]{figures/sweep-entities-robust.pdf}
\end{subfigure}
\caption{Sweeps over values of $\lambda$ for AP (a) and robust (b) runs. $\lambda=0.0$ is the baseline run scored only on the document text, while $lambda=1.0$ is based entirely on the entity text.}
\label{figure.sweeps-ql}
\end{figure*}

\begin{figure}
\centering
\includegraphics[width=.85\columnwidth]{figures/sweep-stanbol.pdf}
\caption{Sweeps over values of $\lambda$ for AP and robust \textit{stanbol} runs.}
\label{figure.sweeps-stanbol}
\end{figure}

@@

As Figure \ref{figure.sweeps-ql} shows, performance of \textit{kb} runs is not very sensitive to $n$, the number of linked entities. Though performance does vary somewhat based on $n$, a run's improvement or decline over the baseline depended only on the mixing parameter $\lambda$, with AP improving at $0.1 \leq \lambda \leq 0.9$ and robust at $0.1 \leq \lambda \leq 0.7$ for all values of $n$. Optimal performance for both collections occured at relatively small numbers of entities as shown in Table \ref{table.performance}; this is a convenient result since it allows for more efficient document expansion.

Notably, our model did not perform well when Stanbol annotations were used as a source of knowledge base links, as seen in Figure \ref{figure.sweeps-stanbol}. Both collections show very slight improvement at $\lambda = 0.1$, but this is not statistically significant and performance declines relative to the baseline at all other values of $\lambda$. We attribute this shortcoming to the overfitting of the Stanbol annotations to specific entity mentions in the text, rather than to concepts relevant to the document. Figure \ref{figure.sweeps-stanbol} does not present sweeps over $n$ for \textit{stanbol} runs because variations in performance at different values of $n$ are negligible using Stanbol entity links. This is due to the low number of linked entities produced by Stanbol: an average of 5.96 and 4.70 per document for AP and robust respectively.

>>>>

We obtain a list of candidate entities by running $Q_D$ over an index of our knowledge base, $C_E$, where each entry in this index is the text of an entity $E$'s knowledge base node. More formally, we rank the entities in $C_E$ against $D$ using Eq. \ref{equation.ql}, substituting $Q_D$ for the query and $E_i$---the text of the $i^{th}$ entity---for the document. Let $\pi_i$ be the log-probability for entity $E_i$ with respect to $D$ given by Eq. \ref{equation.ql}.

@@

To perform knowledge base linking, we make use of the September 1, 2015 dump of English Wikipedia. We build an Indri\footnote{http://www.lemurproject.org/indri/} index over the Wikipedia page text. The text of each page serves as the ``description text'' used in Eq. \ref{eq.entity-sum}.

We test our approach using the TREC 2004 robust topics. These 250 topics are used with data from TREC disks 4 and 5. In addition, we use the AP newswire collection from TREC disks 1 and 2 with topics 101-200. As noted in \cite{Frank2013}, updates to knowledge bases may lag considerably behind the occurrence of events, so using slightly older test collections helps to ensure knowledge base coverage of the topics.

For comparison, we also report the results of our model using entity links produced by Apache Stanbol\footnote{http://stanbol.apache.org/}. We process the test collections with Stanbol's default ``enhancer,'' which supplies entity links and corresponding confidence scores. Stanbol's links to DBpedia\footnote{http://dbpedia.org} generally correspond to Wikipedia pages and may be converted easily. We select the link with the highest confidence for each mention in a given document and limit the set of links to $n$, the number of entities used in our bag-of-links approach. These links form the set of document links, and their confidence scores are normalized to provide an estimate of $P(E|D)$.

@@

We remove stop words in documents and entity descriptions for all runs. For the \textit{kb} and \textit{stanbol} runs, we retrieve the top 1000 documents per query using the default Indri query likelihood implementation. We then re-rank these documents by incorporating their knowledge base links as described in Section \ref{section.model}.

@@

\begin{table}[htb]
\centering
\begin{tabular}{|c|p{0.29\textwidth}|c|} \hline
{\bf Param} & {\bf Meaning} & {\bf Value} \\ \hline
$k$ & The maximum number of document terms to use in constructing $Q_D$. & 20 \\ \hline
$n$ & The maximum number of knowledge base entries in $\mathcal{E}_D$. & 10-100 \\ \hline
$\lambda$ & Mixing parameter controlling the weights of $P(q|D)$ and $P(q|E)$ & 0.0-1.0 \\ \hline
$\mu$ & Used for Dirichlet smoothing of both $P(q|D)$ and $P(q|E)$. & 2500 \\ \hline
%$fbDocs$ & The number of feedback documents to use for RM3 runs. & 20 \\ \hline
%$fbTerms$ & The number of terms per document to use for RM3 runs. & 20 \\ \hline
%$\alpha$ & Mixing parameter controlling the weights of the original query and relevance model for RM3 runs. & 0.5 \\ \hline
\end{tabular}
\caption{Parameter settings for the entity linking procedure and retrieval model}
\label{table.parameters}
\end{table}

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|c|l|c|c|c|} \hline
& {\bf Run} & {\bf $\lambda$} & {\bf $n$} & {\bf MAP} \\ \hline
\rule{0pt}{2.5ex} \multirow{3}{*}{Robust} & {\it baseline-ql} & -- & -- & 0.2183 \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it kb-ql} & 0.2 & 10 & 0.2354$^{\uparrow}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it stanbol-ql} & 0.1 & -- & 0.2194 \\ \hline
\rule{0pt}{2.5ex} \multirow{3}{*}{AP} & {\it baseline-ql} & -- & -- & 0.2346 \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it kb-ql} & 0.2 & 20 & 0.2680$^{\uparrow}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & {\it stanbol-ql} & 0.1 & -- & 0.2355 \\ \hline
\end{tabular}
\caption{The top-scoring runs and baselines by MAP. $\uparrow$ indicates statistically significant improvements over baselines.}
\label{table.performance}
\end{table}

\begin{figure*}[!htb]
\centering
\begin{subfigure}{\columnwidth}
\centering
\includegraphics[width=.9\columnwidth]{figures/sweep-entities-AP.pdf}
\end{subfigure}%
\begin{subfigure}{\columnwidth}
\centering
\includegraphics[width=.9\columnwidth]{figures/sweep-entities-robust.pdf}
\end{subfigure}
%\begin{subfigure}{.5\columnwidth}
%\centering
%\includegraphics[width=\columnwidth]{figures/sweep-stanbol.pdf}
%\caption{Stanbol}
%\end{subfigure}
\caption{Sweeps over values of $\lambda$ for AP (a) and robust (b) \textit{kb} runs. $\lambda=0.0$ is the baseline run scored only on the document text, while $\lambda=1.0$ is based entirely on the entity text.}
\label{figure.sweeps-ql}
\end{figure*}

\begin{figure}[!htb]
\centering
\includegraphics[width=.85\columnwidth]{figures/sweep-stanbol.pdf}
\caption{Sweeps over values of $\lambda$ for AP and robust \textit{stanbol} runs.}
\label{figure.sweeps-stanbol}
\end{figure}

@@

As Figure \ref{figure.sweeps-ql} shows, performance of \textit{kb} runs is not very sensitive to $n$, the number of linked entities: AP shows improvement over baseline at $0.1 \leq \lambda \leq 0.9$ and robust at $0.1 \leq \lambda \leq 0.7$ for all values of $n$. Optimal performance for both collections occurs at relatively small numbers of entities as shown in Table \ref{table.performance}; this is a convenient result since it allows for more efficient document expansion.

Figure \ref{figure.sweeps-stanbol} does not present sweeps over $n$ because variations in performance at different values are negligible for \textit{stanbol} runs. This is due to the low number of entities linked by Stanbol: an average of only 5.96 and 4.70 per document for AP and robust respectively. Notably, our model does not perform well with Stanbol annotations, as seen in Figure \ref{figure.sweeps-stanbol}. Both collections show very slight improvement at $\lambda = 0.1$, but this is not statistically significant and performance declines relative to the baseline at all other values of $\lambda$. We attribute this shortcoming to the overfitting of the Stanbol annotations to specific entity mentions in the text, rather than to concepts relevant to the document.
